\documentclass[autodetect-engine]{jsarticle}

\usepackage[sc]{mathpazo}
\usepackage{newpxtext}
%枠で囲む
\usepackage{ascmac}
\usepackage{amsmath}

\newcommand{\fulltoday}{\number\day\space \ifcase\month\or
  January\or February\or March\or April\or May\or June\or
  July\or August\or September\or October\or November\or December\fi
  \space\number\year}

\title{Prob \& Stats}
\author{Kyoshiro Kamura}
\date{\fulltoday}

\begin{document}
\maketitle

{\fontsize{10.5bp}{16.8bp}\selectfont
  \section{Introduction}
  Prob \& Stats is Not New.
  
  The concept of chance of uncertainty.
  
  \section{Sets and Elements}
  A \textbf{``set''} is clealy defined collection of \textbf{``elements''}.

  Sets are clealy defined, but not nessesarily finite.

  \subsection{Symbols}
  When element ``$a$'' belongs to set ``$A$'', we write
  \[
  a \in A
  \]
  That means ``$a$ is an element of $A$.''.

  If element ``$b$'' is outside set ``$A$'', we write
  \[
  b \notin A
  \]

  If the elements of set $B$ are contained within set $A$
  \[
  B \subset A
  \]
  That means ``$B$ is subset of $A$.''.

  A set containing no elements is called \textbf{``null set''}
  and witten as "$\emptyset$''.

  \subsection*{\underline{Let's consider 2 sets $A$ and $B$}}
  The set created by the elements belonging to both $A$ \& $B$ is called the \textbf{``intersection''}.
  \[
  A \cap B
  \]

  The set created by all the element of $A$ \& $B$ is called the \textbf{``union''}
  \[
  A \cup B
  \]

  All elements outside both $A$ \& $B$ from the ``complementary'' set.
  \[
  \overline{A \cup B} = U - (A \cup B)
  \]
  \begin{itembox}[l]{Note}
    In some textbook, this symbol, ``$U$'' means \textbf{``Everything''}.
  \end{itembox}

  \subsubsection*{\underline{Practice Excercise}}
  \[
  U = \{1, 2, 4, 8, 10\}, A = \{4, 8\}
  \]
  \begin{flushright}
    Note : ``$U$'' is the ``entire universe'', and $A$ is a subset of $U$.
  \end{flushright}

  \begin{flalign*}
    \displaystyle
    &1.\;A \cap U = \{4, 8\}&\\
    &2.\;A \cup U = \{1, 2, 4, 8, 10\}&\\
    &3.\;B = \overline{A} = \{1, 2, 10\}&\\
    &4,\;A \cap B = \emptyset&\\
    &5,\;A \cup B = \{1, 2, 4, 8, 10\}&
  \end{flalign*}

  \subsection{Rules}
  For calucalations with sets, the following equations \textbf{``rules''} are useful.

  \begin{itemize}
  \item Commutative Rule : $A \cup B = B \cup A\;$, $A \cap B = B \cap A$
  \item Associative Rule : $A \cup (B \cup C) = (A \cup B) \cup C\;$, $A \cap (B \cap C) = (A \cap B) \cap C$
  \item Distributive Rule : $A \cap (B \cup C) = (A \cap B) \cup (A \cap C)\;$, $A\cup (B \cap C) = (A \cup B) \cap (A \cup C)$
  \item De Morgan's Rule : $\overline{A \cap B} = \overline{A}\cup\overline{B}\;$, $\overline{A \cup B} = \overline{A} \cap \overline{B}$
  \end{itemize}

  \subsubsection*{\underline{Practice Excercise}}
  $\cdot$Use Venn's Diagram to show De Morgan's Rule 1.
  
  $\cdot$Use Venn's Diagram to show De Morgan's Rule 2.

  \subsubsection*{\textbf{Two Basic Rules}}
  \[\overline{(\overline{A})} = A,\;A\cap\overline{A} = \emptyset\]

  \subsection{How to count the number of elements}
  $n(A)$:number of elements in finite set A
  
  $n(B)$:number of elements in finite set B
  
  $n(A\cup B)$:number of elements in sets A and B

  \underline{\textbf{The way to count the number of elements.}}

  If ther is on overlap.

  \[n(A\cup B) = n(A) + n(B)\]

  but, in case of some counted twice,

  \[n(A\cup B) = n(A) + n(B) - n(A\cap B)\]

  $A\times B$:\textbf{''direct product''} or \textbf{``cartesian product''} means set of all possible ordered pairs.

  \[
  A \times B = \{(a,\;b)|a \in A,\;b \in B\}
  \]

  \[
  n(A\times B) = n(A).n(B)
  \]
  
}

\end{document}
